Highlighting Disputed Claims on the Web

### 2010-02-22 papers/www_disputefinder/disputefinder_final.tex
Minor changes to final version - largely suggested by Beth

%\documentclass{article}
\documentclass{www2010-submission}
\usepackage{times}
%\usepackage{uist}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
%
%\newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
%\newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
%\newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
%\newcommand{\node}[1]{{[\color{blue} NOTE: #1]}}

@@

@@

\toappear

@@

\additionalauthors{Tye Rattenbury and Tad Hirsch, Intel Research Principles and Practices,\texttt{[tye.rattenbury,tad.hirsch]@intel.com}}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/highlight_vaccine_shadow.png}
	\caption{Dispute Finder highlights text snippets that make disputed claims.}
	\label{highlight}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7.5cm]{pictures/popup_vaccine_shadow.png}
	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a ``don't mark this'' button}

@@

On Wikipedia, WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author, Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is, and Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest. These tools have a similar aim to Dispute Finder, but are limited to Wikipedia.

@@

\todo{Improve the paraphraser UI so it shows users what pages are making the claim}
\todo{Improve the ``see examples on the web'' UI to it shows the pages that were found with the activists training work}
\todo{Provide a customized RSS reader and search engine that does dispute tracking. - future work?}
\todo{Should we explicitly list what we think are our key contributions?}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/add_claim_list.png}
	\caption{A user can use this interface to add a new disputed claim manually.}
	\label{add_claim}
	\end{center}
\end{figure}

>>>>

%\documentclass{article}
\documentclass{www2010-accepted}
\usepackage{times}
%\usepackage{uist}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
%\usepackage{letterpaper}

%
%\newcommand{\want}[1]{{[\color{blue} WANT: #1]}}
%\newcommand{\todo}[1]{{[\color{blue} TODO: #1]}}
%\newcommand{\idea}[1]{{[\color{blue} IDEA: #1]}}
%\newcommand{\node}[1]{{[\color{blue} NOTE: #1]}}

@@

\widowpenalty=1000
\clubpenalty=1000

@@

%\special{papersize=8.5in,11in}
%\setlength{\pdfpageheight}{\paperheight}
%\setlength{\pdfpagewidth}{\paperwidth}

%\toappear

@@

\additionalauthors{Tye Rattenbury and Tad Hirsch, Intel Research Principles and Practices,\texttt{[tye.l.rattenbury,tad.hirsch]@intel.com}}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7.5cm]{pictures/highlight_vaccine_shadow.png}
	\caption{Dispute Finder highlights text snippets that make disputed claims.}
	\label{highlight}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8.5cm]{pictures/popup_vaccine_shadow_big.png}
	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a ``don't mark this'' button}

@@

On Wikipedia, WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author, Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is, and WikiScanner.virgil.gr finds cases where a Wikipedia edit has been made by someone with a conflict of interest. These tools have a similar aim to Dispute Finder, but are limited to Wikipedia.

@@

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/add_claim_list.png}
	\caption{Interface to add a new disputed claim manually.}
	\label{add_claim}
	\end{center}
\end{figure}
